Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-19 p2/ordering.tex
Review

\begin{myth}\mlabel{can_simplify}
Each sequence of commands $\wrksx{S}$
can be transformed into a simple sequence
$S^*\eqnrv S$ by applying repeatedly the following transformations:
{\rm(i)} swap neighboring commands on incomparable nodes;
{\rm(ii)} simplify neighboring commands on the same node;
{\rm(iii)} delete assertion commands.
\end{myth}
\begin{proof}
We can remove all assertion commands, as based on
\cref{ax_assert} the resulting sequence extends the original one.
We therefore assume that $S$ contains no assertion commands.

>>>>

\begin{myth}\mlabel{can_simplify}
Each sequence of commands $\wrksx{S}$
can be transformed into a simple sequence
$S^*\eqnrw S$ by applying repeatedly the following transformations:
{\rm(i)} swap neighboring commands on incomparable nodes;
{\rm(ii)} simplify neighboring commands on the same node;
{\rm(iii)} delete assertion commands.
\end{myth}
\begin{proof}
We can remove all assertion commands, as based on
\cref{ax_assert} the resulting sequence extends the original one.
We therefore assume that $S$ contains no assertion commands.

### 2018-07-19 p2/rec-intro.tex
Added conclusion
Review

If we start with two copies of the filesystem $\FS$,
and two different sequences are applied to the copies to yield $\FS_A=A\aFS$
and $\FS_B=B\aFS$, then our aim is to define sequences of commands $\reca$ and $\recb$
so that $\recb\aFS_A$ and $\reca\aFS_B$ would be as close to each other as possible.

@@

\begin{mydef}[Reconciliation]\mlabel{def:reconciliation}
We determine $\reca$---which we apply to $\FS_B$ 
to reconcile it with $\FS_A$---to be
the largest subset of $A\setminus B$
that is independent of $B\setminus A$,
where $A$ and $B$ are simple sequences representing
the updates applied to $\FS$ to arrive at replicas $\FS_A$ and $\FS_B$:
\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \mbox{~and~}  \alpha\indep \bmanp }. \]
$\recb$ can be obtained in a similar way by reversing $A$ and $B$
in the definition.
\end{mydef}

Note that $\alpha$ is not an assertion command, and $\bmanp$ contains no assertion commands;
also, $\alpha\not\in\bmanp$, so independence in this case is equivalent to
the node $\alpha$ affects being incomparable to the nodes commands in $\bmanp$ affect.
Therefore whether two commands are independent is easy to determine programmatically
in at most $O(x^2)$ time, where $x$ is the number of commands. % TODO
Then, to generate the sequence $\reca$ from the resulting set, 
we can order the commands using the algorithm described in
\cref{ordering} as $\reca$, being a subset of $A$, is also simple.

>>>>

If we start with two copies of a filesystem $\FS$,
and two different sequences are applied to the copies to yield $\FS_A=A\aFS$
and $\FS_B=B\aFS$, then our aim is to define sequences of commands $\reca$ and $\recb$
so that $\recb\aFS_A$ and $\reca\aFS_B$ would be as close to each other as possible.

@@

\begin{mydef}[Reconciliation]\mlabel{def:reconciliation}
For two simple sequences $A$ and $B$,
$\reca$ is a valid ordering of
the largest subset of $A\setminus B$
that is independent of $B\setminus A$:
\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \mbox{~and~}  \alpha\indep \bmanp }. \]
$\recb$ can be obtained in a similar way by reversing $A$ and $B$
in the definition.
\end{mydef}

Note that $\alpha\in\reca$ is not an assertion command, and $\bmanp$ contains no assertion commands,
and $\alpha\not\in\bmanp$, therefore $\alpha\indep\bmanp$ is equivalent to
the node $\alpha$ affects being incomparable to the nodes commands in $\bmanp$ affect.
Therefore whether two commands are independent is easy to determine programmatically
in at most $O(x^2)$ time, where $x$ is the number of commands. % TODO
Then, to generate the sequence $\reca$ from the resulting set, 
apply topological sorting according to $\orderrel$ as defined in \cref{ordering}.

### 2018-07-19 p2/upd-correct.tex
Review

\begin{proof}
Let us assume that some mechanism recorded all changes that occurred
to $\FS$ until it reached the state $\FS^*$.
Our set of commands is sufficient to record any change, as
there are commands for every input and output type pair, therefore
we know that the changes can be recorded as a sequence of commands $S$
where $S\aFS=\FS^*$.
($S$ will not contain assertion commands, as they do not
represent an actual change in the filesystem.)
Based on \cref{can_simplify}, there is a simple sequence $S^*$
that extends $S$.

Therefore we know $S^*\aFS=\FS^*$, and that
$\FS^*$ and $\FS$ differ at exactly those nodes that $S^*$ has commands on.
$U$ must also contain commands on the same set of nodes,
and it must contain the same commands,
as for the command $\cxynv$, $[x]$ must be $[\FS(n)]$, and $y$ must be $\FS^*(n)$.
From this we know that $U$ is a permutation of $S^*$ and so $\orderset{U}=\orderset{S^*}$.

As the update detector uses $\orderrel$ to order the commands in $U$, trivially $U\in\orderset{U}$,
which means $U\in\orderset{S^*}$,
and so from \cref{simple_reorder_equiv} we know that $U\equiv S^*$,
from which $U\aFS=\FS^*$.
\end{proof}

>>>>

\begin{proof}
First, we create a sequence of commands $S$ for which $S\aFS=\FS^*$.
First, create a topological sort of all nodes in $\setn$ that are
not empty in $\FS$ so that children come first,
that is, if $n'\descendant n$, then $n$ precedes $n'$.
For each node in the given order, add a destruction command to a sequence $S_0$
that deletes the value at $n$.
We know that the commands will never break the filesystem, as the types of nodes
with empty children can be freely changed, and that $S_0\aFS$ is empty at all nodes.
Next, order nodes in $\setn$ that re not empty in $\FS^*$ in the reverse order,
that is, if $n'\descendant n$, then $n'$ precedes $n$.
Add a construction command to a sequence $S_1$ for each node that changes an empty value
to $\FS^*(n)$.
We know that $S_1$ is defined on an empty filesystem for the same reason,
and clearly $(S_0\cc S_1)\aFS=\FS^*$.
By \cref{can_simplify} there exists a simple $S$ for which $S\eqnrw (S_0\cc S_1)$.

Therefore we know $S\aFS=\FS^*$, and that
$\FS^*$ and $\FS$ differ at exactly those nodes that $S$ has commands on.
$U$ must also contain commands on the same set of nodes,
and it must contain the same commands,
as for the command $\cxynv$, $[x]$ must be $[\FS(n)]$, and $y$ must be $\FS^*(n)$.
From this we know that $U$ is a permutation of $S$ and so $\orderset{U}=\orderset{S}$.

As the update detector uses the $\orderrel$ relation to order the commands in $U$, trivially $U\in\orderset{U}$,
which means $U\in\orderset{S}$,
and so from \cref{simple_reorder_equiv} we know that $U\equiv S$,
from which $U\aFS=\FS^*$.
\end{proof}
